### 2016-01-28 paper/final/source/Levin_JTB_Supplement.tex
In process of drafting Response 3

\usepackage{xr}
\externaldocument{chemokine_main_revised}

@@

An overview of the model implementation is shown in Fig.~\ref{fig:modelchart}.  The model is initialized with one virus-secreting cell placed in the middle of a 2-dimensional sheet of hexagonally-tiled epithelial cells (288,212 total cells).  The sheet measures 5$mm$ per side, which is large enough to contain the infection (Fig.~\ref{fig:cycells}).  The molecular grid (Text S1 1.3) is initialized with a resolution of 20$\mu m$.  Each time step of the model represents 6 seconds.

@@

The model simulates a chemokine gradient surrounding the infected focus (Fig.~\ref{fig:cycells}), based on the calculated per-infected cell secretion rate (Table \ref{tab:strains}) and known chemical parameters for a 10 kDa protein (Table \ref{tab:parameters}).  T cell sensitivity depends on receptor density \citep{Desmetz2006} and this was assumed to be constant.

@@

% we hypothesize that it renders IP-10 ineffectual.  We hypothesize that this leads to the elevated RANTES secretion rates measured in aH5N1 compared to the other two strains (Table \ref{tab:strains}).  Because of this behavior IP-10 was not included in the aH5N1 model runs.

@@

The model parameters were chosen from literature when available and estimated within plausible ranges otherwise (Tables \ref{tab:strains} and \ref{tab:parameters}).  One-factor-at-a-time (OFAT) analysis was performed by varying Individual parameters over ranges of plausible (and sometimes even implausible) values while the rest of the parameter set was held constant.  Each parameter was varied over all three influenza strains, creating three sets of sensitivity plots (Figures~\ref{fig:asensitivity}-\ref{fig:psensitivity}).

We then categorized the model parameters into one of three qualitative groups: parameters that do not affect the model's qualitative behavior (stable parameters), parameters that affect the model's quantitative peak infection size but do not affect final clearance, (peak change parameters), and those parameters that affect the final clearance of the infection (sensitive parameters) (Table \ref{tab:sensitivity}).  Parameters are presented along with their range using the following format:  \\

@@

Stable parameters do not affect the outcome of the infection unless they are adjusted to values outside the realm of possibility.  Specifically, the plausible parameter values in this group are within a range that does not significantly affect the asymptotic behavior of the model.  We further split this group into two categories in Table \ref{tab:sensitivity}, \textit{stable} parameters and \textit{bounded stable} parameters.  \textit{Bounded stable} parameters are only stable within a specific range of values, while \textit{stable} parameters seem to be stable over all the values that were tested.

@@

Compartmental modeling design suggests the removal of such stable parameters.  Due to the nature of the ABM, inclusion of these parameters is mechanistically necessary.  Thus, we include and parameterize them using the methods described in the main paper and Table \ref{tab:parameters}.

@@

An explicit sensitivity analysis was not directly performed.  The range of the parameters are taken from the respective secretion rates of the aH5N1, sH1N1, and pH1N1 influenzas (Table \ref{tab:strains}).

@@

PRCC analysis was performed as described in \cite{Marino2008}.  Samples were generated using Latin hypercube sampling (LHS) to generate 333 sample points for 17 parameters (those from Table \ref{tab:sensitivity}, plus the sH1N1 viral secretion rate).  Each parameter was assigned a confidence distribution (Table \ref{tab:lhs}) and sampled using its inverse cumulative distribution function to generate points with density proportional to the underlying probability distribution function.  Each sample point was evaluated three times using unique random seeds for a total of 999 samples.  One sample point resulted in undefined model behavior and was removed, leaving a total of 996 samples.

Output is defined as the number of infected cells remaining for each time point.  Each model run generates 144,001 time points (10 day model with 6 second time steps).  PRCC analysis was performed over every 100th time point, resulting in a time series of 1441 Spearman rank correlation coefficients ($\rho$) and significance values ($p$) for each parameter (Figs. \ref{fig:prcc} - \ref{fig:vsec}).

@@

Viral infectivity, viral diffusion rate, and viral secretion rate, values of $\rho$ cross or approach zero over time.  This merely reflects that the modeled target cells have died (Fig.~\ref{fig:exhaustive}) and so the decline in $\rho$ is irrelevant.

%This effect is due to the spatial constraints built into our agent based model.  The  model environment was designed to be large enough to contain an infection defined by the default model parameter values.  Extreme values of the viral parameters cause rapid infection growth to the point that the modeled system is exhausted (Fig. \ref{fig:exhaustive}).  In these cases the number of infected cells tends towards zero at later time points as every modeled target cell has died before the model is complete.  Thus, the calculated values of $\rho$ for these given parameters should be trusted only at earlier time points.

@@

\begin{figure}[!ht]
\begin{center}
 \includegraphics[width=\textwidth]{FigureS1}
 \end{center}
\caption{{\bf Preliminary Model 1 fits to data.}  Preliminary Model 1 (Eq. 1) was fit to experimental data (Table~\ref{tab:data}) using a genetic algorithm as described in the main paper.  sH1N1 IP-10 secretion exceeded measurement accuracy above 8500 pg/mL and these three values (empty red triangles) were not included in the model fitting.  RMSE values of the fits can be seen in Table~\ref{tab:rmse}.  IP-10 data and model fits shown in red (triangles), RANTES data and model fits shown in yellow (squares).} 
 \label{fig:fits}
\end{figure}

\begin{figure}[!ht]
\begin{center}
 \includegraphics[width=\textwidth]{Figure_S2}
 \end{center}
\caption{{\bf Varying T cell sensitivity to chemokine.}  H5N1 model results use RANTES  only, and sH1N1 and pH1N1 use both IP-10 and RANTES. Total number of incubating, secreting and apoptotic cells are plotted for each infection.  The sensitivity value specifies the minimum level of chemokine concentration required for T cells to detect it. } 
 \label{fig:sensitivity}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=\textwidth]{Figure_S3}
	\caption{\textbf{Effects of different chemokine combinations.}  A) aH5N1 does not stimulate an IP-10 response.  B-C) sH1N1 and pH1N1 show no significant difference between IP-10 alone versus IP-10 and RANTES combined.}
	\label{fig:chemokine}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S4}
	\caption{\textbf{aH5N1 sensitivity analysis.} The sensitivity analysis results for 16 parameters applied to the aH5N1 model simulation.  In each subgraph, the thicker purple line shows the results of the model using the default parameter value.}
	\label{fig:asensitivity}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S5}
	\caption{\textbf{sH1N1 sensitivity analysis.} The sensitivity analysis results for 16 parameters applied to the sH1N1 model simulation.  In each subgraph, the thicker purple line shows the results of the model using the default parameter value.  The divergence between Apoptosis Time values of 90m and 120m (upper-left plot) highlights an important threshold of infection control.}
	\label{fig:ssensitivity}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S6}
	\caption{\textbf{pH1N1 sensitivity analysis.} The sensitivity analysis results for 16 parameters applied to the pH1N1 model simulation.  In each subgraph, the thicker purple line shows the results of the model using the default parameter value.}
	\label{fig:psensitivity}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S7}
	\caption{\textbf{PRCC sensitivity analysis.} PRCC analysis generated Spearman correlation coefficients ($\rho$) and significance values ($p$) over 1441 time points.  Plots show values of $\rho$ vs. time for each parameter tested.  Dark blue indicates significance levels at $p < 0.01$.  Gold indicates significance of $p < 0.05$.  Light gray indicates $p \geq 0.05$.  Six parameters show significant effect over the time period where they were relevant to model dynamics: infected cell expression time, viral response to IgM, viral infectivity, T cell expected lifetime at the FOI, viral decay rate, and the viral diffusion rate.}
	\label{fig:prcc}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=\textwidth]{Figure_S8}
	\caption{\textbf{PRCC sensitivity analysis for the viral secretion rate.} Similar to Figure S6, PRCC analysis generated Spearman correlation coefficients ($\rho$) and significance values ($p$) over 1441 time points.  Plot shows the values of $\rho$ vs. time for the viral secretion rate.  Dark blue indicates significance levels at $p < 0.01$.  Gold indicates significance of $p < 0.05$.  Light gray indicates $p \geq 0.05$.  Viral secretion shows significant effect on model output.  The decline of $\rho$ over time reflects the early death of every modeled target cell (Figure~\ref{fig:exhaustive})).}
	\label{fig:vsec}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=\textwidth]{Figure_S9}
	\caption{\textbf{Exhaustive Growth:} Certain parameter sets generated by Latin hypercube sampling caused rapid uncontrolled infection growth (Samples 1-3).  This resulted in the early death of every modeled target cell (saturation at day 1) and the inevitable decline of the infection size to zero.  A larger, unbounded model environment would show unconstrained growth.  This effect explains the decline of the $\rho$ value of several viral parameters to or past zero over time in Figures \ref{fig:prcc} and \ref{fig:vsec}.}
	\label{fig:exhaustive}
\end{center}
\end{figure}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|  l  l  l  |}
  \hline
  Population & Description & Initial Value\\
  \hline
  $T$ & Healthy target epithelial cells & 1,000,000 \\
  $I_1$ & Virus-incubating cells & 0 \\
  $I_2$ & Virus-secreting cells & 0 \\
  $V$ & Free virus particles & 10,000 \\
  $F$ & Interferon quantity & 0 \\
  $C$ & Chemokine quantity (ng/mL) & 0 \\
  \hline
  \hline
  Parameter & Description & Value \\
  \hline
  $\beta$ & Viral infection rates &  \\
    & \hspace{2em} Avian & 5.3e-7 (PFU$\cdot$h)$^{-1}$ \\
    & \hspace{2em} Seasonal & 6.1e-7 (PFU$\cdot$h)$^{-1}$ \\
    & \hspace{2em} Pandemic &  2.7e-6 (PFU$\cdot$h)$^{-1}$\\
  $p$ & Viral production rates & \\
    & \hspace{2em} Avian & 0.20 (PFU/h) \\
    & \hspace{2em} Seasonal & 1.4 (PFU/h) \\
    & \hspace{2em} Pandemic & 18.3 (PFU/h) \\
  $e$ & Interferon strengths & \\
    & \hspace{2em} Avian & 1.0e-8 \\
    & \hspace{2em} Seasonal & 1.6e-6 \\
    & \hspace{2em} Pandemic & 3.4e-3 \\
  $\tau_2$ & Interferon production delays &  \\
    & \hspace{2em} Avian & 21.5 (h) \\
    & \hspace{2em} Seasonal & 23.6 (h) \\
    & \hspace{2em} Pandemic & 21.0 (h) \\
  $\delta$ & Virus-secreting cell decay rate & 0.6 (h$^{-1}$) \\
  $d$ & Chemokine decay rate & 1.386 (h$^{-1}$) \\
  $\tau_1$ & Viral incubation time & 10 (h) \\
  $\tau_3$ & Chemokine production delays & \\
    & \hspace{2em} IP-10 & 8 (h)\\
    & \hspace{2em} RANTES & 16 (h)\\
  \hline
\end{tabular}
\caption{\textbf{Parameters for Preliminary Model 1 (Equation 1)}.  All parameters and populations are taken from \citep{Mitchell2011} except for $C$, $d$, and $\tau_3$.  The value chosen for $d$ corresponds to a 30 minute half-life and values for $\tau_3$ were set from the observed chemokine data (Fig.~\ref{fig:data}).  Interferon ($F$) is an abstracted unitless quantity and thus $e$ is a unitless multiplier.}
\label{tab:dde}
\end{center}
\end{table}

\begin{table}[!ht]
\begin{center}
\begin{tabular}{| c | c | c |}
  \hline
  Strain & Chemokine & RMSE \\
  \hline
  \multirow{2}{*}{aH5N1} & RANTES & 166 \\
  & IP-10 & 7,950 \\
  \hline
  \multirow{2}{*}{sH1N1} & RANTES & 90 \\
  & IP-10 & 2,732 \\
  \hline
  \multirow{2}{*}{pH1N1} & RANTES & 2,671  \\
  & IP-10 & 64,342 \\
  \hline
\end{tabular}
\caption{\textbf{Root mean squared error of Preliminary Model 1 fits.}  Preliminary Model 1 (Eq. 1) was fit to experimental data (Table~\ref{tab:data}) using a genetic algorithm as described in the main paper.  The resulting model fits can be seen in Figure~\ref{fig:fits}.}
\label{tab:rmse}
\end{center}
\end{table}

@@

\begin{table}[!ht]
\centering
\begin{tabular}{| c | l | c | l |}
  \hline                        
  Category & Parameter & Units & Distribution \\
  \hline
  \multirow{3}{*}{Chemokine} & Chemokine Decay Rate & \textit{Hz} &  LN(-3.4, 1.0) \\
  & Chemokine Diffusion Rate & \textit{$\mu$m$^2$/s} & LN(-0.5, 1.0) \\
  & Chemokine Secretion Rate & $(pg/s\cdot cell)$ & LN(-3.7, 0.1) \\
  \hline
  \multirow{6}{*}{T Cell} & Circulation Time & \textit{seconds} & LN(-.75, 0.5)\\
  & T Cell Kill Rate & \textit{min} & LN(1.0, 0.5) \\
  & T Cell Speed & \textit{$\mu$m/min} & LN(-.75, 1), \\
  & T Cell Age in Blood & \textit{days} & LN(0.6, 1.0) \\
  & T Cell Age at FOI& \textit{min} & LN(2.1, 0.5) \\
  & T Cell Production Rate & \textit{cells/h} & LN(3.1, 0.15) \\
  \hline
  \multirow{3}{*}{Delay} & Apoptosis Time & \textit{hours} & U(0.0, 2.0) \\
  & Expression Time & \textit{min} & LN(3.0, 0.15) \\
  & Incubation Time & \textit{hours} & LN(-1.0, 0.15) \\
  \hline 
  \multirow{4}{*}{Virus} & Viral Response to IgM & | & LN(1.0, 0.5) \\
  & Infectivity & \textit{min/virion} & LN(2.1, 0.5) \\
  & Viral Decay Rate &  \textit{day$^{-1}$} & LN(0, 1.0) \\
  & Viral Diffusion Rate & \textit{$\mu$m$^2$/s} & LN(-1.5, 1.0) \\
  & Viral Secretion & $(PFU/s\cdot cell)$ & LN(-3.4, 0.3) \\
  \hline  
\end{tabular}
\caption{\textbf{Latin hypercube sampling distributions.}  LHS was used to generate sample points containing each of the 16 parameters from Table \ref{tab:sensitivity}, plus the sH1N1 viral secretion rate.  Parameters were sampled over biologically plausible ranges listed here for use in PRCC analysis.  LN signifies a log-normal distribution.  Values were sampled from a regular normal distribution with the listed parameters and then transformed to linear space from $log_{10}$ space.  U signifies a uniform distribution.}
\label{tab:lhs}
\end{table}

>>>>

@@

An overview of the model implementation is shown in Fig. 2.  The model is initialized with one virus-secreting cell placed in the middle of a 2-dimensional sheet of hexagonally-tiled epithelial cells (288,212 total cells).  The sheet measures 5$mm$ per side, which is large enough to contain the infection (Fig. 5).  The molecular grid (Text S1 1.3) is initialized with a resolution of 20$\mu m$.  Each time step of the model represents 6 seconds.

@@

The model simulates a chemokine gradient surrounding the infected focus (Fig. 5), based on the calculated per-infected cell secretion rate (Table 3) and known chemical parameters for a 10 kDa protein (Table 2).  T cell sensitivity depends on receptor density \citep{Desmetz2006} and this was assumed to be constant.

@@

% we hypothesize that it renders IP-10 ineffectual.  We hypothesize that this leads to the elevated RANTES secretion rates measured in aH5N1 compared to the other two strains (Table 3).  Because of this behavior IP-10 was not included in the aH5N1 model runs.

@@

The model parameters were chosen from literature when available and estimated within plausible ranges otherwise (Tables 1 and 2).  One-factor-at-a-time (OFAT) analysis was performed by varying Individual parameters over ranges of plausible (and sometimes even implausible) values while the rest of the parameter set was held constant.  Each parameter was varied over all three influenza strains, creating three sets of sensitivity plots (Figures~\ref{fig:asensitivity}-\ref{fig:psensitivity}).

We then categorized the model parameters into one of three qualitative groups: parameters that do not affect the model's qualitative behavior (stable parameters), parameters that affect the model's quantitative peak infection size but do not affect final clearance, (peak change parameters), and those parameters that affect the final clearance of the infection (sensitive parameters) (Table 3).  Parameters are presented along with their range using the following format:  \\

@@

Stable parameters do not affect the outcome of the infection unless they are adjusted to values outside the realm of possibility.  Specifically, the plausible parameter values in this group are within a range that does not significantly affect the asymptotic behavior of the model.  We further split this group into two categories in Table 3, \textit{stable} parameters and \textit{bounded stable} parameters.  \textit{Bounded stable} parameters are only stable within a specific range of values, while \textit{stable} parameters seem to be stable over all the values that were tested.

@@

Compartmental modeling design suggests the removal of such stable parameters.  Due to the nature of the ABM, inclusion of these parameters is mechanistically necessary.  Thus, we include and parameterize them using the methods described in the main paper and Table 2.

@@

An explicit sensitivity analysis was not directly performed.  The range of the parameters are taken from the respective secretion rates of the aH5N1, sH1N1, and pH1N1 influenzas (Table 1).

@@

PRCC analysis was performed as described in \cite{Marino2008}.  Samples were generated using Latin hypercube sampling (LHS) to generate 333 sample points for 17 parameters (those from Table 3, plus the sH1N1 viral secretion rate).  Each parameter was assigned a confidence distribution (Table \ref{tab:lhs}) and sampled using its inverse cumulative distribution function to generate points with density proportional to the underlying probability distribution function.  Each sample point was evaluated three times using unique random seeds for a total of 999 samples.  One sample point resulted in undefined model behavior and was removed, leaving a total of 996 samples.

Output is defined as the number of infected cells remaining for each time point.  Each model run generates 144,001 time points (10 day model with 6 second time steps).  PRCC analysis was performed over every 100th time point, resulting in a time series of 1441 Spearman rank correlation coefficients ($\rho$) and significance values ($p$) for each parameter (Figs. S6 - S7).

@@

Viral infectivity, viral diffusion rate, and viral secretion rate, values of $\rho$ cross or approach zero over time.  This merely reflects that the modeled target cells have died (Fig. S8) and so the decline in $\rho$ is irrelevant.

%This effect is due to the spatial constraints built into our agent based model.  The  model environment was designed to be large enough to contain an infection defined by the default model parameter values.  Extreme values of the viral parameters cause rapid infection growth to the point that the modeled system is exhausted (Fig. S8).  In these cases the number of infected cells tends towards zero at later time points as every modeled target cell has died before the model is complete.  Thus, the calculated values of $\rho$ for these given parameters should be trusted only at earlier time points.

@@

\begin{figure}[!ht]
\begin{center}
 \includegraphics[width=\textwidth]{Figure_S-1}
 \end{center}
\caption{{\bf Varying T cell sensitivity to chemokine.}  H5N1 model results use RANTES  only, and sH1N1 and pH1N1 use both IP-10 and RANTES. Total number of incubating, secreting and apoptotic cells are plotted for each infection.  The sensitivity value specifies the minimum level of chemokine concentration required for T cells to detect it. } 
 \label{fig:sensitivity}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=\textwidth]{Figure_S2}
	\caption{\textbf{Effects of different chemokine combinations.}  A) aH5N1 does not stimulate an IP-10 response.  B-C) sH1N1 and pH1N1 show no significant difference between IP-10 alone versus IP-10 and RANTES combined.}
	\label{fig:chemokine}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S3}
	\caption{\textbf{aH5N1 sensitivity analysis.} The sensitivity analysis results for 16 parameters applied to the aH5N1 model simulation.  In each subgraph, the thicker purple line shows the results of the model using the default parameter value.}
	\label{fig:asensitivity}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S4}
	\caption{\textbf{sH1N1 sensitivity analysis.} The sensitivity analysis results for 16 parameters applied to the sH1N1 model simulation.  In each subgraph, the thicker purple line shows the results of the model using the default parameter value.  The divergence between Apoptosis Time values of 90m and 120m (upper-left plot) highlights an important threshold of infection control.}
	\label{fig:ssensitivity}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S5}
	\caption{\textbf{pH1N1 sensitivity analysis.} The sensitivity analysis results for 16 parameters applied to the pH1N1 model simulation.  In each subgraph, the thicker purple line shows the results of the model using the default parameter value.}
	\label{fig:psensitivity}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=9in]{Figure_S6}
	\caption{\textbf{PRCC sensitivity analysis.} PRCC analysis generated Spearman correlation coefficients ($\rho$) and significance values ($p$) over 1441 time points.  Plots show values of $\rho$ vs. time for each parameter tested.  Dark blue indicates significance levels at $p < 0.01$.  Gold indicates significance of $p < 0.05$.  Light gray indicates $p \geq 0.05$.  Six parameters show significant effect over the time period where they were relevant to model dynamics: infected cell expression time, viral response to IgM, viral infectivity, T cell expected lifetime at the FOI, viral decay rate, and the viral diffusion rate.}
	\label{fig:prcc}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=\textwidth]{Figure_S7}
	\caption{\textbf{PRCC sensitivity analysis for the viral secretion rate.} Similar to Figure S6, PRCC analysis generated Spearman correlation coefficients ($\rho$) and significance values ($p$) over 1441 time points.  Plot shows the values of $\rho$ vs. time for the viral secretion rate.  Dark blue indicates significance levels at $p < 0.01$.  Gold indicates significance of $p < 0.05$.  Light gray indicates $p \geq 0.05$.  Viral secretion shows significant effect on model output.  The decline of $\rho$ over time reflects the early death of every modeled target cell (Figure S8).}
	\label{fig:vsec}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
	\includegraphics[width=\textwidth]{Figure_S8}
	\caption{\textbf{Exhaustive Growth:} Certain parameter sets generated by Latin hypercube sampling caused rapid uncontrolled infection growth (Samples 1-3).  This resulted in the early death of every modeled target cell (saturation at day 1) and the inevitable decline of the infection size to zero.  A larger, unbounded model environment would show unconstrained growth.  This effect explains the decline of the $\rho$ value of several viral parameters to or past zero over time in Figures S6 and S7.}
	\label{fig:exhaustive}
\end{center}
\end{figure}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|  l  l  l  |}
  \hline
  Population & Description & Initial Value\\
  \hline
  $T$ & Healthy target epithelial cells & 1,000,000 \\
  $I_1$ & Virus-incubating cells & 0 \\
  $I_2$ & Virus-secreting cells & 0 \\
  $V$ & Free virus particles & 10,000 \\
  $F$ & Interferon quantity & 0 \\
  $C$ & Chemokine quantity (ng/mL) & 0 \\
  \hline
  \hline
  Parameter & Description & Value \\
  \hline
  $\beta$ & Viral infection rates &  \\
    & \hspace{2em} Avian & 5.3e-7 (PFU$\cdot$h)$^{-1}$ \\
    & \hspace{2em} Seasonal & 6.1e-7 (PFU$\cdot$h)$^{-1}$ \\
    & \hspace{2em} Pandemic &  2.7e-6 (PFU$\cdot$h)$^{-1}$\\
  $p$ & Viral production rates & \\
    & \hspace{2em} Avian & 0.20 (PFU/h) \\
    & \hspace{2em} Seasonal & 1.4 (PFU/h) \\
    & \hspace{2em} Pandemic & 18.3 (PFU/h) \\
  $e$ & Interferon strengths & \\
    & \hspace{2em} Avian & 1.0e-8 \\
    & \hspace{2em} Seasonal & 1.6e-6 \\
    & \hspace{2em} Pandemic & 3.4e-3 \\
  $\tau_2$ & Interferon production delays &  \\
    & \hspace{2em} Avian & 21.5 (h) \\
    & \hspace{2em} Seasonal & 23.6 (h) \\
    & \hspace{2em} Pandemic & 21.0 (h) \\
  $\delta$ & Virus-secreting cell decay rate & 0.6 (h$^{-1}$) \\
  $d$ & Chemokine decay rate & 1.386 (h$^{-1}$) \\
  $\tau_1$ & Viral incubation time & 10 (h) \\
  $\tau_3$ & Chemokine production delays & \\
    & \hspace{2em} IP-10 & 8 (h)\\
    & \hspace{2em} RANTES & 16 (h)\\
  \hline
\end{tabular}
\caption{\textbf{Parameters for Preliminary Model 1 (Equation 1)}.  All parameters and populations are taken from \citep{Mitchell2011} except for $C$, $d$, and $\tau_3$.  The value chosen for $d$ corresponds to a 30 minute half-life and values for $\tau_3$ were set from the observed chemokine data (Fig. 3).  Interferon ($F$) is an abstracted unitless quantity and thus $e$ is a unitless multiplier.}
\label{tab:dde}
\end{center}
\end{table}

@@

\begin{table}[!ht]
\centering
\begin{tabular}{| c | l | c | l |}
  \hline                        
  Category & Parameter & Units & Distribution \\
  \hline
  \multirow{3}{*}{Chemokine} & Chemokine Decay Rate & \textit{Hz} &  LN(-3.4, 1.0) \\
  & Chemokine Diffusion Rate & \textit{$\mu$m$^2$/s} & LN(-0.5, 1.0) \\
  & Chemokine Secretion Rate & $(pg/s\cdot cell)$ & LN(-3.7, 0.1) \\
  \hline
  \multirow{6}{*}{T Cell} & Circulation Time & \textit{seconds} & LN(-.75, 0.5)\\
  & T Cell Kill Rate & \textit{min} & LN(1.0, 0.5) \\
  & T Cell Speed & \textit{$\mu$m/min} & LN(-.75, 1), \\
  & T Cell Age in Blood & \textit{days} & LN(0.6, 1.0) \\
  & T Cell Age at FOI& \textit{min} & LN(2.1, 0.5) \\
  & T Cell Production Rate & \textit{cells/h} & LN(3.1, 0.15) \\
  \hline
  \multirow{3}{*}{Delay} & Apoptosis Time & \textit{hours} & U(0.0, 2.0) \\
  & Expression Time & \textit{min} & LN(3.0, 0.15) \\
  & Incubation Time & \textit{hours} & LN(-1.0, 0.15) \\
  \hline 
  \multirow{4}{*}{Virus} & Viral Response to IgM & | & LN(1.0, 0.5) \\
  & Infectivity & \textit{min/virion} & LN(2.1, 0.5) \\
  & Viral Decay Rate &  \textit{day$^{-1}$} & LN(0, 1.0) \\
  & Viral Diffusion Rate & \textit{$\mu$m$^2$/s} & LN(-1.5, 1.0) \\
  & Viral Secretion & $(PFU/s\cdot cell)$ & LN(-3.4, 0.3) \\
  \hline  
\end{tabular}
\caption{\textbf{Latin hypercube sampling distributions.}  LHS was used to generate sample points containing each of the 16 parameters from Table 3, plus the sH1N1 viral secretion rate.  Parameters were sampled over biologically plausible ranges listed here for use in PRCC analysis.  LN signifies a log-normal distribution.  Values were sampled from a regular normal distribution with the listed parameters and then transformed to linear space from $log_{10}$ space.  U signifies a uniform distribution.}
\label{tab:lhs}
\end{table}
